Solar wind discontinuities spatial evolution in the outer heliosphere

### 2024-05-28 article.qmd
update

---
title: Solar wind discontinuities spatial evolution in the outer heliosphere
author:
  - name: Zijin Zhang
    email: zijin@ucla.edu
    orcid: 0000-0002-9968-067X
    affiliation: University of California, Los Angeles
    roles: writing
    corresponding: true
  - name: Anton V. Artemyev
    email: aartemyev@igpp.ucla.edu
    orcid: 0000-0001-8823-4474
    affiliation: University of California, Los Angeles
  - name: Vassilis Angelopoulos
    orcid: 0000-0001-7024-1561
    affiliation: University of California, Los Angeles
  - name: Shi Chen
    orcid: 0000-0002-2582-7085
    affiliation: University of California, Los Angeles
affiliations:
  - id: ucla
    name: University of California, Los Angeles
execute: 
  eval: false
code-links:
  - href: ../
    text: Website
  - repo
  - href: https://www.overleaf.com/project/65b0a9c80a3616adf6e599e8
    text: Overleaf
abstract: We present a study of the spatial evolution of solar wind discontinuities in the outer heliosphere using data from the Juno spacecraft during its cruise phase. We identify and analyze the properties of the discontinuities at different radial distances from the Sun. By differentiating the temporal effect (correlated with solar activity) and spatial variations (correlated with radial distance), we find that (1) the normalized occurrence rate of IDs drops with the radial distance from the Sun, following a $1/r$ law; (2) The thickness of IDs increases with the radial distance from the Sun, but after normalization to the ion inertial length, the thickness of IDs decreases; (3) The current intensity of IDs decreases with the radial distance from the Sun, but after normalization to the Alfven current, the current intensity of IDs increases.
---

@@

@marianiStatisticalStudyMagnetohydrodynamic1983
@marianiVariationsOccurrenceRate1973

@@

1. The normalized occurrence rate of IDs drops with the radial distance from the Sun, following $1/r$ law.
2. The thickness of IDs increases with the radial distance from the Sun, but after normalization to ion inertial length, the thickness of IDs slightly decreases. The thickness distribution of IDs remains almost constant with the year of observation.
3. The current density of IDs decrease with the radial distance from the Sun, but after normalization to the Alfven current , the current density of IDs slightly increases. The current density distribution of IDs slightly increases with the year of observation, but after normalization, the current density distribution remains identical across the five years.

>>>>

---
title: Solar wind discontinuities spatial evolution in the outer heliosphere
author:
  - name: Zijin Zhang
    email: zijin@ucla.edu
    orcid: 0000-0002-9968-067X
    affiliation: University of California, Los Angeles
    roles: writing
    corresponding: true
  - name: Anton V. Artemyev
    email: aartemyev@igpp.ucla.edu
    orcid: 0000-0001-8823-4474
    affiliation: University of California, Los Angeles
  - name: Vassilis Angelopoulos
    orcid: 0000-0001-7024-1561
    affiliation: University of California, Los Angeles
affiliations:
  - id: ucla
    name: University of California, Los Angeles
execute: 
  eval: false
code-links:
  - href: ../
    text: Website
  - repo
  - href: https://www.overleaf.com/project/65b0a9c80a3616adf6e599e8
    text: Overleaf
abstract: We present a study of the spatial evolution of solar wind discontinuities in the outer heliosphere using data from the Juno spacecraft during its cruise phase. We identify and analyze the properties of the discontinuities at different radial distances from the Sun. By differentiating the temporal effect (correlated with solar activity) and spatial variations (correlated with radial distance), we find that (1) the normalized occurrence rate of IDs drops with the radial distance from the Sun, following a $1/r$ law; (2) The thickness of IDs increases with the radial distance from the Sun, but after normalization to the ion inertial length, the thickness of IDs decreases; (3) The current intensity of IDs decreases with the radial distance from the Sun, but after normalization to the Alfven current, the current intensity of IDs increases.
---

@@

@marianiStatisticalStudyMagnetohydrodynamic1983
@tsurutaniInterplanetaryDiscontinuitiesTemporal1979
@marianiVariationsOccurrenceRate1973

@@

1. The normalized occurrence rate of IDs drops with the radial distance from the Sun, following $1/r$ law.
2. The thickness of IDs increases with the radial distance from the Sun, but after normalization to ion inertial length, the thickness of IDs slightly decreases. The thickness distribution of IDs remains almost constant with the year of observation.
3. The current density of IDs decrease with the radial distance from the Sun, but after normalization to the Alfven current , the current density of IDs slightly increases. The current density distribution of IDs slightly increases with the year of observation, but after normalization, the current density distribution remains identical across the five years, thus no effect of the long-term (i.e. solar cycle) temporal variations.
